\vspace{-2cm} \LARGE Divergence-Free Smoothed Particle Hydrodynamics \\ \large Advanced Simulation and Visualization of Fluids in Computer Graphics

### 2017-01-15 report/paper.tex
added cylinder collision fig and text

	When the application starts, the water is represented as set of spheres where every sphere has the properties of a particle.
	The initial state is illustrated in Figure~\ref{fig:res1}
	The water is affected by a gravity which induce a falling motion, illustrated in Figure~\ref{fig:res2}.

@@

    % Results from adding cylinder

>>>>

	When the application starts, the water is represented as set of spheres where every sphere has the properties of a particle.
	The initial state is illustrated in Figure~\ref{fig:res1}.
	The water is affected by a gravity which induce a falling motion, illustrated in Figure~\ref{fig:res2}.

@@

    % Results from adding cylinder
    Implicit geometries can also be added to the scene in order to see how the water collides and interacts with it. Figure \ref{fig:res5} illustrates a scene with a solid cylinder that forces the water to divert its momentum around the cylinder's surface.

    \begin{figure}[h!]
        \includegraphics[width=\linewidth]{img/cylinder2.png}
        \caption{The water colliding with a cylinder.}
        \label{fig:res5}
    \end{figure}
